Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-08-18 analysis/exp2_analysis.Rmd
adding developmental zoom data so far
latest online children drop data analysis

---
title: "Drop Exp. 2 Analysis"
author: "George"
date: "7/20/2020"
output: html_document
---

@@

>>>>

---
title: "Exp. 2 Analysis: 2AFC, adults vs. children"
author: "George"
date: Sys.Date()
output: html_document
---

@@

```{r}
rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'

cd <- rawch %>% filter(Exclude!="Y") %>% 
  dplyr::select(-Version, -Torus0, -Exclude, -Qual1, -Qual2, -Notes)

# make long
#cdl <- cd %>% pivot_longer()

# first 10 columns are

for(i in 3:ncol(cd)) {
  tt = table(cd[,i])
  bt = binom.test(tt, p=.5, alternative="two.sided")
  cat(names(cd)[i], ' ', sum(tt), ' p=', round(bt$p.value,3))
  print(round(tt / sum(tt), 2))
}

```

```{r}
hist(cd$Age)
```

```{r}

```
